\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-09 Response.tex

%    If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
%    This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$. As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded. Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}. 
%\end{correction}
%
%Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
%\begin{correction}
%    If \( c \) is chosen such that
%    \begin{gather}
%        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
%    \end{gather}
%    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
%\end{correction}

\item \textit{Typo in eq. (40).}

@@

The bounds on \( c \) have been modified due to the additional detail in the stability proof shown in~\Cref{proof:adaptive_control}.

The equation has been modified as:
\begin{correction}
\begin{gather*}
	0 < c < \min \braces{\sqrt{\frac{2 \lambda_m k_R n_1}{\lambda_M^2}},
	%\sqrt{\frac{2 k_R n_2}{\lambda_M}}, 
	\frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}}. %\label{eqn:c_bound}
\end{gather*}
\end{correction}
